%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Hugo Chen}
\address{Songshan District \linebreak Taipei, Taiwan R.O.C.}
\contacts{+886-988537425 \linebreak hugo.chen731@gmail.com }

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Engineer}{Telexpress}{Sep 2018 -- Present}
			\textbf{Voice Bot (Python)}
			\begin{itemize}
				\item Voice Bot is a real time streaming low latency bi-directional system which integrates the PBX telephony system and text-based chatbot service.
				\item Lead backend developer responsible for system design, database design, implementing server and telephony system clients, and organizing  three other engineers for internal tools development and QA testing.
				\item Voice Bot is powered by asynchronous Socket.IO framework to stream audio data from telephony system back to the server and perform speech recognition.
				\item Developed dynamic voice activity detection algorithm to further improve the user experience.
				\item Voice Bot is using MongoDB as database, redis as cache, and ELK as logging system. 
				\item Developing a key words correction algorithm to reduced 40\% character error rate.
				\item Further improve the key words detection rate by 28.6\% by building a customized ASR system.
				\item Developed a gender recognition based in voice and implemented on the voice chatbot system with 98\% accuracy.
			\end{itemize}
			\textbf{Chatbot (Python)}
			\begin{itemize}
				\item Developed a text data augmentation system which combine several algorithms.
				\item Integrated SOTA NLP algorithm BERT to improve chatbot performance.
			\end{itemize}
			\textbf{E-Commerce Platform (.Net Core)}
			\begin{itemize}
				\item Developed backend microservice APIs for the platform.
				\item Integrated open source BI tool into the platform.
				\item Implemented business partner's decrypt algorithms in open source BI tool.
			\end{itemize}
			\textbf{Customer Service Online Chat (.Net Framework)}
			\begin{itemize}
				\item Developed a new chatting channel on WeChat.
				\item Implemented business parter's decrypt algorithms in the system (Java).
			\end{itemize}
			\textbf{DevOps}
			\begin{itemize}
				\item Compile docker-compose yaml configurations for defining and running multi-container e-commerce platform microservices.
				\item Compile Kubernetes yaml configurations using Helm for automating deployment, scaling, and management of containerized e-commerce platform microservices.
				\item Setting up Jenkins pipelines for automated CI/CD.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{ShortUrl}  A highly scalable url shortener service to reduce a long link. Using flask, MongoDB, Redis, and host on DigitalOcean.
				\item \textbf{PhotoRater}  An ios app written in swift which using Tensorflow to train a photo rating model and transfer to a Tensorflow Lite model and integrated in to the app.
				\item \textbf{Insult Puppy}  A frontend practice project in which the insult contents come from Evil Insult Generator API and the Puppies images come from RandomDog API. Developed using Vue. Host on Netlify.
				\item \textbf{Game of Life}  In memory of Dr. John Horton Conway. Developed using Python, SciPy, and OpenCV.
				\item \textbf{freqtrade-gym}  OpenAi custom gym environment in order to train reinforcement learning agents to profit in crypto markets.
				\item \textbf{Kaggle Competitions:}
					\begin{itemize}
						\item Google Cloud \& YouTube-8M Video Understanding Challenge: Top 15\% Bronze Medal.
						\item Statoil/C-CORE Iceberg Classifier Challenge: Top 14\%.
						\item Mercedes-Benz Greener Manufacturing: Top 15\%.
					\end{itemize}
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Yunlin, Taiwan R.O.C.}{National Yunlin University of Sciences and Technology}{Sep 2016 -- Aug 2018}
			\bigskip
			\begin{itemize}
				\item M.S.E. in Computer Science and Information Engineering, Fall 2018.  GPA: 4.0
				\item Thesis: “Semi-supervised Learning Using Generative Adversarial Networks”
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Taoyuan, Taiwan R.O.C.}{Chang Gung College}{Sep 2011 -- June 2015}
			\begin{itemize}
				\item B.S.E. in Computer and Information Science, May 2015. 
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Programming Languages:}  Python (fluent), C\# .NET Core/Framework (proficient), SQL (proficient), JavaScript (proficient), Shell Script(proficient), Swift(prior experience), C/C++(prior experience), Java(prior experience).
				\item \textbf{Technologies:}  Git, Docker, Flask, MongoDB, Redis, MySQL, Microsoft SQL Server, Vue, Tensorflow, PyTorch, Kaldi, OpenCV.
				\item \textbf{Cloud Platforms:}  Google Cloud Platform, Azure, DigitalOcean, Netlify.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
